Preprints in Ecology \& Evolution

### 2012-08-28 ms.tex
merge + table

\begin{figure}[ht!]

\centering\includegraphics[width=0.50\textwidth]{map.pdf}
\caption
{
    Since the time between submission and
}
\label{fig:map}

\end{figure}

@@

% A table?
%% Journal | Publisher | ISI rank | Official policy ?

>>>>

\begin{figure}[ht!]
\centering\includegraphics[width=0.50\textwidth]{map.pdf}
\caption
{
    Since the time between submission and ...
}
\label{fig:map}
\end{figure}

@@

\begin{table*}
    \centering
    \begin{tabular}{|lll|}
    \hline
    Journal                 			&   Publisher                           & Policy \\
    \hline
    \emph{All journals}     			& Springer                            	& OK \\
    \emph{All journals}     			& BMC                                 	& OK \\
    \emph{All journals}            		& Elsevier                            	& OK \\
    \emph{All journals}            		& Nature Publishing Group             	& OK \\
    \emph{All journals}            		& Public Library of Science           	& OK \\
    \emph{All journals}            		& Science                             	& Ambiguous \\
    \emph{All journals}            		& Ecological Society of America       	& OK \\
    \emph{All journals}            		& Royal Society                       	& OK \\
    Ecology Letters						& Wiley-Blackwell                   	& Refuse \\
    Evolution   						& Wiley-Blackwell                     	& ? \\
    Journal of Evolutionary Biology 	& Wiley-Blackwell   					& ? \\
    The American Naturalist 			& University of Chicago Press           & OK \\
    \hline
    \end{tabular}
    \caption{Policies for many publishers and some specific journals in ecology
\& evolution.}
    \label{table:policies}
\end{table*}
